% Marvin Charles's Resume
% Created: Thu Sep 20 13:00:24 EDT 2007
% Last Modified: Thu Oct  4 19:49:24 EDT 2007

\documentclass[11pt,oneside]{article}
\usepackage{geometry}
\usepackage[T1]{fontenc}

\pagestyle{empty}
\geometry{letterpaper,tmargin=.75in,bmargin=.75in,lmargin=.75in,rmargin=.75in,headheight=0in,headsep=0in,footskip=.3in}

\setlength{\parindent}{0in}
\setlength{\parskip}{0in}
\setlength{\itemsep}{0in}
\setlength{\topsep}{0in}
\setlength{\tabcolsep}{0in}

% Name and contact information
\newcommand{\name}{Marvin Charles}
\newcommand{\addr}{3215 Avenue H, Apt. 12G, Brooklyn, NY 11210}
\newcommand{\phone}{(718) 866-8424}
\newcommand{\email}{marvin.charles@gmail.com}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% New commands and environments

%Sets the default top level list bullet style
\renewcommand{\labelitemi}{$\diamond$}

% This defines how the name looks
\newcommand{\bigname}[1]{
	\begin{center}\fontfamily{phv}\selectfont\LARGE\scshape#1\end{center}
}

% A ressection is a main section (<H1>Section</H1>)
\newenvironment{ressection}[1]{
	\vspace{4pt}
	{\fontfamily{phv}\selectfont\large\scshape#1}
	\begin{itemize}
	\vspace{3pt}
}{
	\end{itemize}
}

% A resitem is a simple list element in a ressection (first level)
\newcommand{\resitem}[1]{
	\vspace{-5pt}
	\item \begin{flushleft} #1 \end{flushleft}
}

% A ressubitem is a simple list element in anything but a ressection (second level)
\newcommand{\ressubitem}[1]{
	\vspace{-2pt}
	\item \begin{flushleft} #1 \end{flushleft}
}

% A resbigitem is a complex list element for stuff like jobs and education:
%  Arg 1: Name of company or university
%  Arg 2: Location
%  Arg 3: Title and/or date range
\newcommand{\resbigitem}[3]{
	\vspace{-5pt}
	\item
	\textbf{#1}---#2 \\
	\textit{#3}
}

% This is a list that comes with a resbigitem
\newenvironment{ressubsec}[3]{
	\resbigitem{#1}{#2}{#3}
	\vspace{-2pt}
	\begin{itemize}
}{
	\end{itemize}
}

\newcommand{\ressubsecnoitems}[3]{
	\resbigitem{#1}{#2}{#3}
	\vspace{-2pt}
}

% This is a simple sublist
\newenvironment{reslist}[1]{
	\resitem{\textbf{#1}}
	\vspace{-5pt}
	\begin{itemize}
}{
	\end{itemize}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Now for the actual document:

\begin{document}

\fontfamily{ppl} \selectfont

% Name with horizontal rule
\bigname{\name}

\vspace{-8pt} \rule{\textwidth}{1pt}

\vspace{-1pt} {\small\itshape \addr \hfill \phone; \email}

\vspace{12 pt}


%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{ressection}{Objective}

%	\resitem{To obtain a software development position where I can continue building on my domain knowledge and best practices while utilizing my academic and technical skills.}

%\end{ressection}


%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Education}

	\begin{ressubsecnoitems}{Polytechnic Institute of NYU}{Brooklyn, NY}{MS in Computer Science: Expected May, 2011 \textbf{--GPA: 3.96}}
	\end{ressubsecnoitems}

	\begin{ressubsecnoitems}{Brooklyn College of the City University of New York}{Brooklyn, NY}{BS in Computer and Information Science: May, 2008 \textbf{--GPA: 3.79 (overall), 3.9 (CIS major)}}
		%\ressubitem{GPA: 3.79 (overall), 3.9 (CIS major)}
	\end{ressubsecnoitems}

\end{ressection}

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Certification}

	\resitem{\textbf{Sun Certified Programmer for the Java Platform (SCJP)}, Standard Edition 6}

\end{ressection}

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Technical Skills}

	%\resitem{\textbf{Environments:} Linux , Mac OS  X, Windows-NT/2000/XP}

	\resitem{\textbf{Programming Languages:} C\#, CSS, HTML, Java, JavaScript, Perl, PHP, Python, SQL}

	\resitem{\textbf{Frameworks and API:} EJB 3, JPA, JSF 2.0, JSP, Servlets, Spring 2.5}
	
	%\resitem{\textbf{Frameworks and API:} JDBC, JQuery, JSF/JSP, Code Igniter, CakePHP, Servlets, Struts, Spring MVC}
	\resitem{\textbf{Application Servers:} GlassFish, Apache Tomcat }
	\resitem{\textbf{Databases:} Oracle, MySql }

\end{ressection}

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Relevant Experience}
	\begin{ressubsec}{Goldman Sachs}{New York, NY}{Technology Summer Analyst: June, 2010--Aug 2010}
		\ressubitem{Implemented application entitlement framework for bank loan servicing application.}
		\ressubitem{Designed and implemented a dashboard for tracking external agent metrics.}
	\end{ressubsec}
	
	\begin{ressubsec}{7thOnline}{New York, NY}{Software Engineer I: May, 2008--Sept 2009}
		\ressubitem{Part of a team responsible for developing and maintaining the company's  web based Assortment Planning and Size Optimization SaaS solution.}
		%\ressubitem{Facilitated application upgrade from J2EE 1.4 to Java EE 5.}
		\ressubitem{Collaborated with Business Analysts to design requested application enhancements.}
		%\ressubitem{Worked with Quality Assurance team located in China on bug resolution.}
		\ressubitem{Provided production support for deployed application.}
		\ressubitem{Facilitated Tomcat cluster upgrade.}
		\ressubitem{Automated system administration tasks and performed ad-hoc reporting.}
		%\ressubitem{Wrote ANT scripts to automate building and pushing development branch code from SVN to development environment.}
		%\ressubitem{\textbf{Technologies:} Oracle 9i, Tomcat, Java, JDBC, JavaMail, Servlets, JSP, HTML, JQuery, CSS, Perl, SVN}
	\end{ressubsec}
	
	\begin{ressubsec}{Andiamo Partners}{New York, NY}{IT Analyst Intern: November, 2007--April, 2008}
		\ressubitem{Part of a team responsible for re-implementing internal and external job source applications.}
		%\ressubitem{Developed new in-place edit interfaces to enable more fluid user interaction.}
		\ressubitem{Lead the initiative to modularize applications by utilizing the MVC pattern.}
		%\ressubitem{\textbf{Technologies:} LAMP, HTML, JQuery, CSS}
		%\ressubitem{Vetted a suitable PHP framework.}
	\end{ressubsec}
	
	\begin{ressubsec}{Brooklyn College Bridges Institute}{Brooklyn, NY}{Web Developer: June, 2006--May 2008}
		\ressubitem{Designed and implemented institute website using PHP, XHTML, CSS and JavaScript. }
		\ressubitem{Developed the back-end data store using MySQL.}
	\end{ressubsec}
	
	%\begin{ressubsec}{CAMBA}{Brooklyn, NY}{Application Developer: December, 2006--May, 2007}
	%	\ressubitem{Designed and implemented a web based helpdesk application in ASP.NET.}
	%	\ressubitem{Implemented membership and role management providers.}
	%	\ressubitem{Developed back-end data store using SQL Server.}
	%\end{ressubsec}

\end{ressection}

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Achievements and Activities}
	%\resitem{Member of Golden Key International Honour Society (2008).}
	
	\resitem{Member of Brooklyn College RoboCup Soccer team (2007 - 2008).}
	
	\resitem{Habitat for Humanity (2006 - Present) -- Most Outstanding Skilled Volunteer (2007).}

	\resitem{Member of the Association for Computing Machinery (2005 - present).}
	
	\resitem{Member of Upsilon Pi Epsilon International Honor Society (2005 - present).}

	\resitem{Student member of the Undergraduate Curriculum Committee (2004).}
	%\resitem{Received departmental scholarship for academic excellence (2004 \& 2008).}


\end{ressection}

%\begin{ressection}{References}
%	\resitem{Available upon request.}
%\end{ressection}

\end{document}
